\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-18 manuscript.Rmd
Library Management

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja","crsh/citr", "masiraji/tabledown")
pacman::p_install_gh("masiraji/tabledown")

>>>>

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")

#if you dont have LaTeX installed run the following line
#tinytex::install_tinytex()
```
